\documentclass{article}

\usepackage{geometry}
\geometry{left=12mm, right=12mm, top=10mm, bottom=16mm}
\usepackage{hyperref}

\usepackage{graphicx}
\usepackage{ulem}
\usepackage{amssymb}

\usepackage{enumitem}
\setlist[itemize]{itemsep=1pt, topsep=1pt, partopsep=1pt, after=\vspace{4pt}}
\setlist[description]{itemsep=1pt, topsep=1pt, parsep=0pt}


\usepackage[T1]{fontenc}

\usepackage{titlesec}
\titleformat{\section}{\normalfont\large\bfseries\scshape\color{primary}}{}{0em}{}[\vspace{-3pt}\titlerule]
\titlespacing*{\section}{0pt}{1.5ex plus 0.5ex minus 0.2ex}{2ex plus 0.2ex}

\usepackage{xparse}
\usepackage{xcolor}



\begin{document}
\setlength{\parindent}{0pt}
\definecolor{primary}{HTML}{004696}

\begin{center}
  {\Large \bf \color{primary} Kaito Baba}\\[2pt]

  Email: \texttt{k.ai.to47802@gmail.com}, \texttt{baba-kaito662@g.ecc.u-tokyo.ac.jp}

  Homepage: \texttt{\url{https://kaito47802.github.io}}

  GitHub: \texttt{\url{https://github.com/kAIto47802}} (Total stars: 332)
  \hspace{1mm}
  Google Scholar: \texttt{\href{https://scholar.google.com/citations?user=oJvSC5wAAAAJ}{oJvSC5wAAAAJ}} (Citations: 115)
\end{center}


\section{Education}

\textbf{The University of Tokyo, Graduate School of Information Science and Technology}
\hspace{\fill}Tokyo, Japan\\
Master of Information Science and Technology
\hspace{\fill}Apr. 2025--Mar. 2027 (expected)\\
\textit{Supervisor: Prof. Hideki Nakayama}
\vspace{2mm}

\textbf{The University of Tokyo}
\hspace{\fill}Tokyo, Japan\\
Bachelor of Engineering in Mathematical Engineering and Information Physics
\hspace{\fill}Apr. 2021--Mar. 2025\\
\textit{Supervisor: Prof. Taiji Suzuki}


\section{Publications}

\NewDocumentCommand{\pubitem}{s m m m m o}{
  \IfBooleanTF{#1}{\item[\small$\bigstar$\hspace{-1.2pt}]}{\item} #2. \IfValueTF{#6}{\href{#6}{#3}}{#3}. \textit{#4}, #5.
}

\rightline{\small $\bigstar$: Featured publications}

\textbf{International Conference Proceedings (Refereed)}
\begin{itemize}
  \pubitem{%
    Daichi Sato, Duc Minh Vo, Khan Md. Anwarus Salam, Hidenori Shoji, Yuma Matsuoka, Takara Taniguchi, \underline{Kaito Baba}, and Hideki Nakayama%
  }{%
    LAVA Challenge 2025: Advancing Japanese Document Understanding with a Challenging PDF-VQA Benchmark%
  }{%
    The 33rd ACM International Conference on Multimedia%
  }{%
    2025%
  }%
    [https://dl.acm.org/doi/10.1145/3746027.3761994]
  %
  %
  %
  %
  %
  \pubitem*{%
    \underline{Kaito Baba}, Wataru Nakata, Yuki Saito, and Hiroshi Saruwatari%
  }{%
    The T05 System for the VoiceMOS Challenge 2024: Transfer Learning from Deep Image Classifier to Naturalness MOS Prediction of High-Quality Synthetic Speech%
  }{%
    IEEE Spoken Language Technology Workshop (SLT)%
  }{%
    2024%
  }%
    [https://ieeexplore.ieee.org/document/10832315]
  (%
  %
    \href{%
      https://github.com/sarulab-speech/UTMOSv2%
    }{%
      GitHub stars: 306%
    }%
  %
  , %
  %
    \href{%
      https://scholar.google.com/citations?view_op=view_citation\&hl=en\&user=oJvSC5wAAAAJ\&citation_for_view=oJvSC5wAAAAJ:u5HHmVD_uO8C
    }{%
      Cited by: 88%
    }%
  %
  )%
\end{itemize}

\textbf{Workshop Papers at International Conferences (Refereed)}
\begin{itemize}
  \pubitem*{%
    \underline{Kaito Baba}, Chaoran Liu, Shuhei Kurita, and Akiyoshi Sannai%
  }{%
    Prover Agent: An Agent-Based Framework for Formal Mathematical Proofs%
  }{%
    ICML Workshop on AI for Math%
  }{%
    2025%
  }[https://arxiv.org/abs/2506.19923]
  (%
  %
    \href{%
      https://github.com/kAIto47802/Prover-Agent%
    }{%
      GitHub stars: 22%
    }%
  %
  , %
  %
    \href{%
      https://scholar.google.com/citations?view_op=view_citation\&hl=en\&user=oJvSC5wAAAAJ\&citation_for_view=oJvSC5wAAAAJ:9yKSN-GCB0IC
    }{%
      Cited by: 21%
    }%
  %
  )%
  \pubitem{%
    \underline{Kaito Baba}, Ryota Yagi, Junichiro Takahashi, Risa Kishikawa, and Satoshi Kodera%
  }{%
    JRadiEvo: A Japanese Radiology Report Generation Model Enhanced by Evolutionary Optimization of Model Merging%
  }{%
    NeurIPS Workshop on AIM-FM: Advancements In Medical Foundation Models: Explainability, Robustness, Security, and Beyond%
  }{%
    2024%
  }[https://arxiv.org/abs/2411.09933]
  (%
  %
  %
  %
    \href{%
      https://scholar.google.com/citations?view_op=view_citation\&hl=en\&user=oJvSC5wAAAAJ\&citation_for_view=oJvSC5wAAAAJ:u-x6o8ySG0sC
    }{%
      Cited by: 5%
    }%
  %
  )%
  \pubitem{%
    Junichiro Takahashi, JingChuan Guan, Masataka Sato, \underline{Kaito Baba}, Kazuto Haruguchi, Daichi Nagashima, Satoshi Kodera, and Norihiko Takeda%
  }{%
    Application of Contrastive Learning on ECG Data: Evaluating Performance in Japanese and Classification with Around 100 Labels%
  }{%
    NeurIPS Workshop on AIM-FM: Advancements In Medical Foundation Models: Explainability, Robustness, Security, and Beyond%
  }{%
    2024%
  }[https://arxiv.org/abs/2504.09302]
  %
  %
  %
  %
  %
\end{itemize}

\textbf{Preprints}
\begin{itemize}
  \pubitem{%
    \underline{Kaito Baba} and Satoshi Kodera%
  }{%
    Multi-Modal Multi-Agent Reinforcement Learning for Radiology Report Generation: Radiologist-Like Workflow with Clinically Verifiable Rewards%
  }{%
    arXiv preprint arXiv:2603.16876%
  }{%
    2026%
  }[https://arxiv.org/abs/2603.16876]
  %
  %
  %
  %
  %
  \pubitem*{%
    \underline{Kaito Baba}, Yoshihiko Ozaki, and Shuhei Watanabe%
  }{%
    Conditional PED-ANOVA: Hyperparameter Importance in Hierarchical \& Dynamic Search Spaces%
  }{%
    arXiv preprint arXiv:2601.20800%
  }{%
    2026%
  }[https://arxiv.org/abs/2601.20800]
  %
  %
  %
  %
  %
\end{itemize}

\textbf{Articles}
\begin{itemize}
  \pubitem{
    \underline{Kaito Baba}%
  }{%
    [Optuna v4.5] Gaussian Process-Based Sampler (GPSampler) Can Now Perform Constrained Multi-Objective Optimization%
  }{%
    Medium%
  }{%
    2025%
  }[https://medium.com/optuna/optuna-v4-5-81e78d8e077a]
  \pubitem{
    \underline{Kaito Baba}%
  }{%
    [Optuna v4.2] Gaussian Process-Based Sampler Can Now Handle Inequality Constraints%
  }{%
    Medium%
  }{%
    2025%
  }[https://medium.com/optuna/optuna-v4-2-gaussian-process-based-sampler-can-now-handle-inequality-constraints-a4f68e8ee810]
\end{itemize}

\textbf{Domestic Conference Proceedings}
\begin{itemize}
  \pubitem{
    Daichi Sato, Duc Minh Vo, Khan Md. Anwarus Salam, Hidenori Shoji, Yuma Matsuoka, Takara Taniguchi, \underline{Kaito Baba}, and Hideki Nakayama%
  }{%
    LAVA Challenge: Benchmarking Japanese-English Document Understanding with Large Vision-Language Models%
  }{%
    28th Meeting on Image Recognition and Understanding (MIRU)%
  }{%
    2025%
  }
  \pubitem{
    \underline{Kaito Baba}, Wataru Nakata, Yuki Saito, and Hiroshi Saruwatari%
  }{%
     UTMOSv2: Integrated Use of Spectrogram and SSL Features for Naturalness MOS Prediction%
  }{%
    Acoustical Society of Japan Autumn Meeting%
  }{%
    2024%
  }
    (\href{%
      https://github.com/sarulab-speech/UTMOSv2%
    }{%
      GitHub stars: 306%
    })
\end{itemize}

\section{Awards and Honors}
\begin{description}[labelwidth=16mm, labelsep=1em, leftmargin=!, font=\normalfont]
  \item[--Aug. 2024] 4 solo bronze medals in Kaggle competitions
  \begin{itemize}[topsep=-2pt]
    \item Won 4 solo bronze medals so far in Kaggle, the world's largest machine learning competition.
  \end{itemize}
  \item[Jun. 2024] \textbf{1st place} in 7 out of 16 metrics and \textbf{2nd place} in the remaining 9 metrics in the VoiceMOS Challenge 2024 Track1
  \begin{itemize}[topsep=-2pt]
    \item Took the above ranking in a global competition to create a machine learning model to predict the naturalness MOS of synthetic speech.
  \end{itemize}
  \item[Mar. 2024] \textbf{1st Place} in  Hackathon by AIFUL (aihack2024)
  \begin{itemize}[topsep=-2pt]
    \item Developed a machine learning model for predicting the credit score of individuals.
  \end{itemize}
  \item[Oct. 2023] Special Prize, \textbf{3rd Place} in Hackathon by LIFECARD
  \begin{itemize}[topsep=-2pt]
    \item Created a machine learning model for credit scoring.
  \end{itemize}
  \item[Sep. 2023] \textbf{World Rank 3} in CodinGame Othello AI competition
  \begin{itemize}[topsep=-2pt]
    \item Developed an AI for the game of Othello (Reversi) by combining deep reinforcement learning and heuristic search algorithms.
  \end{itemize}
  \item[Mar. 2023] Special Prize, \textbf{4th Place} in the Final Round in Hackathon by SoftBank
  \begin{itemize}[topsep=-2pt]
    \item Developed a web application integrated with object detection AI.
  \end{itemize}
\end{description}


\section{Work Experience}

\textbf{Preferred Networks, Inc.}
\hspace{\fill}Tokyo, Japan\\
\textit{Part-time Engineer}
\hspace{\fill}Jul. 2024--Present
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Developing Optuna, an hyperparameter optimization library, as part of the AutoML team.
\end{itemize}

\textbf{The University of Tokyo Hospital}
\hspace{\fill}Tokyo, Japan\\
\textit{Technical Staff (Part-time)}
\hspace{\fill}May. 2024--Present
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Conducting research and development of medical AI in collaboration with physicians.
\end{itemize}

\textbf{SIGNATE Inc.}
\hspace{\fill}Tokyo, Japan\\
\textit{Technical Advisor, Educational Material Creator (Outsourcing)}
\hspace{\fill}Dec. 2023--May. 2024
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Created materials on RAG (Retrieval-Augmented Generation) and prompt engineering as an LLM Advisor.
  \item Created educational materials on data analysis, LLM usage, algorithms, optimization, etc.
\end{itemize}

\textbf{kuzen Inc.}
\hspace{\fill}Tokyo, Japan\\
\textit{Full-stack Engineer (Internship)}
\hspace{\fill}Nov. 2023--Apr. 2024
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Involved in front-end and back-end implementation, as well as the development of a RAG system using LangChain.
\end{itemize}

\textbf{Recruit Co., Ltd}
\hspace{\fill}Tokyo, Japan\\
\textit{Datascientist (Internship)}
\hspace{\fill}Oct. 2023--Dec. 2023
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Worked in the Search Group of the Data Promotion Office, developing a RAG system to improve the internal document search experience.
\end{itemize}

\textbf{The University of Tokyo Edge Capital Partners Co., Ltd. (UTEC)}
\hspace{\fill}Tokyo, Japan\\
\textit{Research Assistant}
\hspace{\fill}Jul. 2023--Apr. 2025
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Conducted data collection, analysis, and predictive model creation for investors.
  \item Developed a system for an internal tool.
\end{itemize}

\textbf{LearnWiz Inc.}
\hspace{\fill}Tokyo, Japan\\
\textit{Font-end Engineer (Outsourcing)}
\hspace{\fill}Apr. 2023--Sep. 2023
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Carried out front-end implementation and proposed UI/UX design for web applications.
\end{itemize}

\textbf{GHELIA Inc.}
\hspace{\fill}Tokyo, Japan\\
\textit{AI Researcher (Internship)}
\hspace{\fill}Jan. 2023--Sep. 2023
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Conducted research and development in deep learning related to image recognition.
\end{itemize}


\section{Other Experience}

\textbf{Sorbonne University}
\hspace{\fill}Paris, France\\
\textit{Internship}
\hspace{\fill}Feb. 2026--Apr. 2026\\
Laboratoire d’informatique de Sorbonne Université (LIP6)
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Worked with Prof. Evripidis Bampis.
  \item Conducted research on learning-augmented algorithms.
\end{itemize}

\textbf{National Tsing Hua University}
\hspace{\fill}Hsinchu, Taiwan\\
\textit{Short-term Exchange Program}
\hspace{\fill}Feb. 2025--Mar. 2025\\
Department of Industrial Engineering and Engineering Management
\begin{itemize}[parsep=0pt, after=\vspace{5pt}]
  \item Worked with Prof. Wing-Kai Hon.
  \item Conducted research on efficient algorithm design.
\end{itemize}


\section{Technical Skills}

\begin{itemize}[parsep=-2pt]
  \item Deal with:
  \begin{itemize}[parsep=0pt, after=\vspace{5pt}]
    \item Deep learning, reinforcement learning, front-end development, back-end development, etc.
  \end{itemize}
  \item Languages and Frameworks:
  \begin{itemize}[parsep=0pt, after=\vspace{5pt}]
    \item Advanced:\\
      Rust, Python, PyTorch, TensorFlow, TypeScript, JavaScript, React, Next.js, HTML/CSS, C, C++, bash, Swift, Go, Google Apps Script, and R
    \item Intermediate:\\
      Haskell, OCaml, Scheme, Assembly (RISC-V), SQL, Fortran, Verilog, C\# (Unity), Julia, Java, and Kotlin
  \end{itemize}
  \item Tools:
  \begin{itemize}[parsep=0pt, after=\vspace{5pt}]
    \item Git/GitHub, Docker, AWS, GCP, Linux, GitHub Actions, GraphQL, Terraform, Arduino, Raspberry Pi, etc.
  \end{itemize}
\end{itemize}


\section{Certifications}

\begin{itemize}
  \item Deep Learning for ENGINEER Certified by JDLA (Japan Deep Learning Association) (2023)
  \item The SUKEN Test in Mathematics Proficiency Grade 1 (2022)
\end{itemize}

\end{document}